Untitled

### 2024-03-19 Markdown/Manuscript/Child_RMDs/MS_Tables_2.Rmd
v4

---
title: "Predr_Cors"
author: "Author"
date: "`r Sys.Date()`"
output: html_document
---
```{r timelygls, tab.cap='Transparent, reusable and updatable (TRU) computational health economic models (CHEMs) are suggestive of ethical modelling practice', tab.id = 'timelygls', echo = F, results = 'asis', warning=FALSE}
library(kableExtra)  
df <- data.frame(` ` = c("Transparent", "Reusable", "Updatable"),
                 `Social acceptability` = c("Modeller judgments, model features and verification checks can be reviewed by third parties.",
                                                                        "Models can be modified to reflect alternative value judgments.",
                                                                        "Models can be modified to reflect alternative value judgments."),
                 `Fitness for purpose` = c("Modeller judgments, model features and verification checks can be reviewed by third parties.","Third party use increases likelihood of errors being identified.","Models can be validly used for longer."),
                 `Beneficial use` = c("Decision-makers can understand the strengths and weakness of models before applying them.","Can inform more decision problems, in more contexts with less duplicative effort.","Models can be validly used for longer."),
                 check.names = F)
if(params$X@outp_formats_chr[1] == "Word") {
  library("flextable")
  library("ftExtra")
  df %>%
    ready4show::print_table(output_type_1L_chr = params$X@outp_formats_chr[1],
                            caption_1L_chr = knitr::opts_current$get("tab.cap"),
                            mkdn_tbl_ref_1L_chr = paste0("tab:",knitr::opts_current$get("tab.id")),
                            use_rdocx_1L_lgl = ifelse(params$X@outp_formats_chr[1]=="Word",T,F),
                            add_to_row_ls = NULL,
                            sanitize_fn = NULL) %>%
    ftExtra::colformat_md()
  }else{
    # library(huxtable)
    # library(dplyr)
    #flextable::set_flextable_defaults() #fonts_ignore=TRUE
    # flextable::flextable(df) %>%
    #   flextable::border_inner(border = officer::fp_border(style = "none")) %>%
    #   flextable::border_outer() %>%
    #   flextable::align(align = "center", part = "header") %>%
    #   flextable::merge_h() %>%
    #   flextable::merge_v() %>%
    #   flextable::valign(j=2, valign = "top") %>%
    #   flextable::align(j=2:4, align = "center") %>%
    #   flextable::bold(j=1, part = "all") %>%
    #   flextable::bold(part = "header") %>%
    #   flextable::width(j = 1, width = 1.2) %>%
    #   flextable::width(j = 2:4, width = 1.6)
    # %>%
    #   
      #flextable::merge_at(i=2,j=1:2)
    # huxtable::as_hux(df) %>% 
    #   #insert_row("MPG-DISP", "", "", "HP-WT", fill = "") %>% 
    #   #huxtable::merge_cells(2:3,1) %>% 
    #  # huxtable::set_header_rows(1, TRUE) %>% 
    #   huxtable::set_col_width(c(.1,.1,.1,.7)) %>%
    #   huxtable::set_wrap(1, value=T)
      #huxtable::style_headers(bold = TRUE)
    df %>%
      kableExtra::kbl(booktabs = T,
                      escape = F,
                      caption = knitr::opts_current$get("tab.cap")) %>%
      kableExtra::kable_paper(full_width = F) %>%
      kableExtra::column_spec(1, bold=T) %>%
      kableExtra::add_header_above(c(" ", "Project team responsibility" = 3), bold = T, italic = T) %>%
      kableExtra::column_spec(2, width = "13em") %>%
      kableExtra::column_spec(3, width = "13em") %>%
      kableExtra::column_spec(4, width = "13em") %>%
      kableExtra::collapse_rows(columns = 2, latex_hline = "none")
      # kableExtra::column_spec(3, width = "35em") %>%
      # kableExtra::pack_rows("Accountable - it is easy to see who developed, tested and applied a model and how they did it.",1,7) %>%
      # kableExtra::pack_rows("Updatable - a model and its components are maintained and continuously improved.",17,20) %>%
      # # kableExtra::pack_rows("Modular - models and their components can be combined to extend their scope",11,12) %>%
      # # kableExtra::pack_rows("Epitomising - model code can be re-used in other decision contexts",13,15) %>%
      # kableExtra::pack_rows("Reusable - a model and its components can be used in other models and by other modellers.",8,16) #%>%
      # kableExtra::pack_rows("Yielding - a model can be simply, flexibly and reliably used as a decision aid",19,20)
    }
```

>>>>

---
title: "Predr_Cors"
author: "Author"
date: "`r Sys.Date()`"
output: html_document
---
```{r timelygls, tab.cap='Transparent, reusable and updatable (TRU) computational health economic models (CHEMs) are suggestive of ethical modelling practice', tab.id = 'timelygls', echo = F, results = 'asis', warning=FALSE}
library(kableExtra)  
df <- data.frame(` ` = c("Transparent", "Reusable", "Updatable"),
                 `Social acceptability` = c("Modeller judgments, model features and verification checks can be reviewed by third parties.",
                                                                        "Models can be modified to reflect alternative value judgments.",
                                                                        "Models can be modified to reflect alternative value judgments."),
                 `Fitness for purpose` = c("Modeller judgments, model features and verification checks can be reviewed by third parties.","Third party use increases likelihood of errors being identified.","Models can be validly used for longer."),
                 `Beneficial use` = c("Decision-makers can understand the strengths and weakness of models before applying them.","Can inform more decision problems, in more contexts with less duplicative effort.",""#"Models can be validly used for longer."
                                      ),
                 check.names = F)
 library("flextable")
  library("ftExtra")
if(params$X@outp_formats_chr[1] == "Word") {

  df %>%
    ready4show::print_table(output_type_1L_chr = params$X@outp_formats_chr[1],
                            caption_1L_chr = knitr::opts_current$get("tab.cap"),
                            mkdn_tbl_ref_1L_chr = paste0("tab:",knitr::opts_current$get("tab.id")),
                            use_rdocx_1L_lgl = ifelse(params$X@outp_formats_chr[1]=="Word",T,F),
                            add_to_row_ls = NULL,
                            sanitize_fn = NULL) %>%
    ftExtra::colformat_md()
  }else{
    # library(huxtable)
    # library(dplyr)
   # flextable::set_flextable_defaults() #fonts_ignore=TRUE
    flextable::flextable(df) %>%
      # flextable::border_inner(border = officer::fp_border(style = "none")) %>%
      # flextable::border_outer() %>%
      flextable::align(align = "center", part = "header") 
    # %>%
    #   flextable::merge_at(i = 3, j = 3:4)
      # flextable::merge_h() %>%
      # flextable::merge_v() %>%
      # flextable::valign(j=2, valign = "top") %>%
      # flextable::align(j=2:4, align = "center") %>%
      # flextable::bold(j=1, part = "all") %>%
      # flextable::bold(part = "header") %>%
      # flextable::width(j = 1, width = 1.2) %>%
      # flextable::width(j = 2:4, width = 1.6)
    # %>%
    #   
      #flextable::merge_at(i=2,j=1:2)
    # huxtable::as_hux(df) %>% 
    #   #insert_row("MPG-DISP", "", "", "HP-WT", fill = "") %>% 
    #   #huxtable::merge_cells(2:3,1) %>% 
    #  # huxtable::set_header_rows(1, TRUE) %>% 
    #   huxtable::set_col_width(c(.1,.1,.1,.7)) %>%
    #   huxtable::set_wrap(1, value=T)
      #huxtable::style_headers(bold = TRUE)
    # df %>%
    #   kableExtra::kbl(booktabs = T,
    #                   escape = F,
    #                   caption = knitr::opts_current$get("tab.cap")) %>%
    #   kableExtra::kable_paper(full_width = F) %>%
    #   kableExtra::column_spec(1, bold=T) %>%
    #   kableExtra::add_header_above(c(" ", "Project team responsibility" = 3), bold = T, italic = T) %>%
    #   kableExtra::column_spec(2, width = "13em") %>%
    #   kableExtra::column_spec(3, width = "13em") %>%
    #   kableExtra::column_spec(4, width = "13em") %>%
    #   kableExtra::collapse_rows(columns = 2, latex_hline = "none")

    }
```

### 2024-03-19 Markdown/Manuscript/Child_RMDs/MS_Tables_3.Rmd
v4

---
title: "Predr_Cors"
author: "Author"
date: "`r Sys.Date()`"
output: html_document
---
```{r cpkgs, tab.cap='Software framework R libraries', tab.id = 'cpkgs', echo = F, results = 'asis'}
library(kableExtra)  
df <- tibble::tibble(Package = c("ready4",
                                       "ready4fun",
                                       "ready4class",
                                       "ready4pack",
                                       "ready4use",
                                       "ready4show"),
                     Purpose = c("Provides a template model module and novel syntax and tools for finding interoperable CHEM modules, datasets and reproducible analysis programs.",
                                 "Streamline and standardise the authoring and documenting of functions that support selective reuse of model algorithms.",
                                 "Streamline and standardise the authoring and documenting of new CHEM modules.",
                                 "Help bundle and disseminate CHEM modules as documented, licensed and quality assured  R libraries.",
                                 "Help manage the labelling and transfer of data between CHEM modules and local and remote data repositories.",
                                 "Support the authoring of programs that implement integrated and reproducible data ingest, analysis and reporting pipelines."),
                           # A = c("3","2-3","2","1-2,5,7","1-2,7","4,6"), 
                           # R = c("4","5","4-5","1,3,6","3,7",""),
                           # U = c("","","","1-3","1",""),
                           `R library dependencies` = Package %>%
                             purrr::map(~ {
                               utils::packageDescription(.x) %>%
                                 `[`(c("Depends", "Imports")) %>%
                                 purrr::map(~{
                                   if(is.null(.x)){
                                     character(0)
                                     }else{
                                       .x %>%
                                         strsplit(",\\n") %>%
                                         purrr::flatten_chr() %>%
                                         purrr::map(~strsplit(.x,", ") %>%
                                                      purrr::flatten_chr()) %>%
                                         purrr::flatten_chr() %>% sort() %>%
                                         purrr::discard(~startsWith(.x,"R "))
                                       }
                                   }) %>%
                                 purrr::flatten_chr() %>%
                                 unique() %>%
                                 sort() %>%
                                 purrr::map_chr(~{
                                   updated_1L_chr <- stringr::str_replace_all(.x,"\\n"," ")
                                   problem_idx_1L_chr <- stringr::str_locate(updated_1L_chr," ")[1,1] %>%
                                     unname()
                                   if(!is.na(problem_idx_1L_chr))
                                     updated_1L_chr <- updated_1L_chr %>%
                                     stringr::str_sub(end = problem_idx_1L_chr-1)
                                   updated_1L_chr %>% 
                                     trimws(which = "left") 
                                   })
                               }) %>% 
                             purrr::map_chr (~ .x %>% paste0(collapse = " "))) %>% 
  as.data.frame() 
# if(params$X@outp_formats_chr[1] != "Word"){
#       df$Ref <- c(rep("",6)
#        # "@ready42022","@ready4fun2022","@ready4class2022","@ready4pack2022","@ready4use2022","@ready4show2022"
#                   )
# }else{
#   df$Ref <- ""
# }

df <- df %>%
  # dplyr::mutate(Standard = purrr::pmap_chr(df,
  #                                          ~paste0("A",
  #                                                 ..3,
  #                                                 paste0(rep("&nbsp;",
  #                                                     2+max(nchar(df[,3]))-nchar(..3)),
  #                                                     collapse = ""#
  #                                                     ),
  #                                                 ifelse(..4=="","","R"),
  #                                                 ..4,
  #                                                 paste0(rep("&nbsp;",
  #                                                     2+max(nchar(df[,4]))-nchar(..4)),
  #                                                     collapse = ""#
  #                                                     ),
  #                                                 ifelse(..5=="","","U"),
  #                                                 ..5,
  #                                                 paste0(rep("&nbsp;",
  #                                                     1+max(nchar(df[,5]))-nchar(..5)),
  #                                                     collapse = ""#
  #                                                     )#,
  #                                                 ))) %>%

  dplyr::select(Package,
                #Ref,
                Purpose,
                #Standard,
                `R library dependencies`)

names_chr <- names(df)
# df <- data.frame(df[,1],
#                  rep(ifelse(params$X@outp_formats_chr[1] == "Word"," ","&nbsp; &nbsp; &nbsp;"),
#                      nrow(df)),
#                  df[,2#:3
#                     ],
#                  rep(ifelse(params$X@outp_formats_chr[1] == "Word"," ","&nbsp; &nbsp; &nbsp;")
#                      ,nrow(df)),
#                  #df[,4],
#                  #rep("&nbsp; &nbsp; &nbsp;",nrow(df)),
#                  df[,3#5
#                     ])
# colnames(df) <- c("Package",
#                   ifelse(params$X@outp_formats_chr[1] == "Word","XXX"," "),
#                   #"Ref", 
#                   "Purpose", 
#                   ifelse(params$X@outp_formats_chr[1] == "Word","YYY"," "),
#                   #"Standard     ",# " ",
#                   "R library dependencies")
#df$Package <- "![](../Data/images/ready4.png){ width=10% }"#"\\includegraphics[valign=T,scale=2.5,raise=2mm]{../Data/images/ready4.png}"
#df$`Standard     `  <- df$`Standard     ` %>% stringr::str_replace_all("&nbsp;"," ")
if(params$X@outp_formats_chr[1] == "Word") {
  library("flextable")
  library("ftExtra")
  df %>% #[,c(1,3:4,6:7)] %>%
    ready4show::print_table(output_type_1L_chr = params$X@outp_formats_chr[1],
                            caption_1L_chr = knitr::opts_current$get("tab.cap"),
                            mkdn_tbl_ref_1L_chr = paste0("tab:",knitr::opts_current$get("tab.id")),
                            use_rdocx_1L_lgl = ifelse(params$X@outp_formats_chr[1]=="Word",T,F),
                            add_to_row_ls = NULL,
                            sanitize_fn = NULL) %>%
    ftExtra::colformat_md()
  }else{
    #df$Ref<-NULL
    #df$Package <- ""
    # df$Package  <- df$Package %>% 
    #                   purrr::map_chr(~paste0("\\includegraphics[valign=M,width=1.9cm,raise=4mm]{../Data/images/",.x,"_logo.png}"))#scale=0.4,raise=3mm]
    # df$Package <- "\\includegraphics[valign=M,scale=0.08,raise=3mm]{../Data/images/ready4.png}"
    #df[,c(1,3,5:6)]   %>%
    df %>%
    # kableExtra::kbl(format = "markdown",
    #                   escape = F,
    #                 caption = knitr::opts_current$get("tab.cap"))
      kableExtra::kbl(booktabs = T, 
                      escape = F,
                      caption = knitr::opts_current$get("tab.cap")) %>%
      kableExtra::kable_paper(full_width = F) %>%
      kableExtra::column_spec(2, width = "20em", latex_valign = "m") %>%
      # kableExtra::column_spec(1, 
      #                         image = kableExtra::spec_image(rep("../Data/images/ready4.png",nrow(df)), 
      #                                                           150, 150)) %>%
      kableExtra::column_spec(3, width = "20em",
                              latex_valign = "m")
    }
```

>>>>

---
title: "Predr_Cors"
author: "Author"
date: "`r Sys.Date()`"
output: html_document
---

\renewcommand{\arraystretch}{2}
```{r trucrit, tab.cap='Criteria for assessing the transparency, reusability and updatability of CHEMs', tab.id = 'cpkgs', echo = F, results = 'asis'}
library(kableExtra) 
df <- data.frame(Attribute = c(rep("Transparent",2), rep("Reusable",2), rep("Updtatable",2)),
                 Item = c("T","R","U") %>% purrr::map(~paste0(.x,1:2)) %>% purrr::flatten_chr(),
                 Criterion = c("Software files (executable code, testing procedures and outcomes and non-confidential data) are publicly available.",
                               "It is easy to see who funded, developed and tested each part of the CHEM and to identify the modelling team’s assumptions, judgments and theories about CHEM development and use.",
                               "Programming practices facilitate selective reuse of model sub-components.",
                               "Licenses allow anyone to ethically reuse model code and non-confidential data, in whole or in part, without charge, and for purposes that include the creation of derivative works.",
                               "Maintenance infrastructure is in place to support version control and collaboration with model users.",
                               "Each new release of a CHEM is systematically retested, with changes implemented to minimise disruptions for existing model users."))
if(params$X@outp_formats_chr[1] == "Word") {
  library("flextable")
  library("ftExtra")
  df %>%
    ready4show::print_table(output_type_1L_chr = params$X@outp_formats_chr[1],
                            caption_1L_chr = knitr::opts_current$get("tab.cap"),
                            mkdn_tbl_ref_1L_chr = paste0("tab:",knitr::opts_current$get("tab.id")),
                            use_rdocx_1L_lgl = ifelse(params$X@outp_formats_chr[1]=="Word",T,F),
                            add_to_row_ls = NULL,
                            sanitize_fn = NULL) %>%
    ftExtra::colformat_md()
  }else{
    df %>%
      kableExtra::kbl(booktabs = T, 
                      escape = F,
                      linesep = "\\addlinespace",
                      caption = knitr::opts_current$get("tab.cap")) %>%
      kableExtra::kable_paper(full_width = F) %>%
      #kableExtra::pack_rows("Resource requirements implications",1,4, hline_after = T) %>%
      #kableExtra::pack_rows("Ethical implications",5,14, hline_after = T) %>%
      kableExtra::column_spec(1, width = "8em", bold=T) %>% #, latex_valign = "m"
      kableExtra::column_spec(2, width = "3em") %>%
      kableExtra::column_spec(3, width = "28em") %>%
      kableExtra::collapse_rows(columns = 1, latex_hline = "major") 
    # %>%
    #   kableExtra::kable_styling(latex_options = "striped")
      # kableExtra::pack_rows("Accountable - it is easy to see who developed, tested and applied a model and how they did it.",1,7) %>%
      # kableExtra::pack_rows("Updatable - a model and its components are maintained and continuously improved.",17,20) %>%
      # kableExtra::pack_rows("Modular - models and their components can be combined to extend their scope",11,12) %>%
      # kableExtra::pack_rows("Epitomising - model code can be re-used in other decision contexts",13,15) %>%
      # kableExtra::pack_rows("Reusable - a model and its components can be used in other models and by other modellers.",8,16) #%>%
      # kableExtra::pack_rows("Yielding - a model can be simply, flexibly and reliably used as a decision aid",19,20)

    }
```

### 2024-03-19 Markdown/Manuscript/Child_RMDs/MS_Tables_4.Rmd
v4

                               "T2 Project team contributions and judgments are easily identified", 

@@

                               "R2 Licenses restrict only unethical reuse",

@@

                               "U2 New releases are systematically retested and deprecated"),

>>>>

                               "T2 Developer contributions and judgments on appropriate use are easily identified", 

@@

                               "R2 Licenses permit reuse and derivative works",

@@

                               "U2 Releases are systematically retested and deprecated"),
